Detection and partial characterisation of stellar multiplicity with Gaia

### 2018-07-03 article/ms.tex
bah

\begin{abstract}
The properties and occurrence rate of stellar multiples (e.g., binaries, triples) 
underpins much of astrophysics. Precisely measuring these quantities is challenging
and observationally demanding. Here we use \Gaia\ data to detect and partially 
characterise \NumberOfStellarMultiples\ stellar multiple systems based on excess 
astrometric jitter, excess radial velocity jitter, the absence of reported radial
velocities, photometry, and intrinsic luminosity.
\todo{We show that astrometric and radial velocity jitter can be calibrated to
estimate inclination angles (and directly constrain companion masses) for thousands 
of systems.}
Comparisons with literature surveys on stellar multiplicity demonstrate that we 
reliably detect binary systems with orbital periods up to $\approx$3.5\,yr. 
\todo{A comment on stellar multiplicity with stellar metallicity.}
\todo{A comment on stellar multiplicity in the field relative to clusters.}
\todo{A comment on systems with stellar remnants (e.g., NS/BHs).}
\end{abstract}

@@

\subsection{Unresolved near-equal mass binaries: photometry}
\label{sec:pb_methods}

If a binary system is observed nearly face-on (at an inclination angle 
$i \approx 0^\circ$) then there is will be no detectable excess radial 
velocity variations. In principle there may be detectable astrometric
variations, but most near-equal mass binaries would be detected more 
reliably through intrinsic magnitudes that are anomalously lower (brighter)
and bluer colours than what would be expected for a single star system.

\todo{How the fuck am I going to model this, exactly?}

>>>>

\begin{abstract}
The properties and occurrence rate of stellar multiples (e.g., binaries, triples) 
underpins much of astrophysics. 
%Precisely measuring these quantities is challenging and observationally demanding. 
Here we use \Gaia\ data to detect and partially 
characterise \NumberOfStellarMultiples\ stellar multiple systems based on excess 
jitter in astrometry and radial velocity.
Comparisons with literature surveys on stellar multiplicity demonstrate that we 
reliably detect binary systems with orbital periods up to $\approx$3.5\,yr. 
We use eclipsing binary systems to calibrate excess astrometric jitter with
tangential motion, allowing us to estimate inclination angles and directly constrain
companion masses for millions of systems.
\todo{A comment on stellar multiplicity with stellar metallicity.}
\todo{A comment on stellar multiplicity in the field relative to clusters.}
\todo{A comment on systems with stellar remnants (e.g., NS/BHs).}
\end{abstract}

@@

%\subsection{Unresolved near-equal mass binaries: photometry}
%\label{sec:pb_methods}

%If a binary system is observed nearly face-on (at an inclination angle 
%$i \approx 0^\circ$) then there is will be no detectable excess radial 
%velocity variations. In principle there may be detectable astrometric
%variations, but most near-equal mass binaries would be detected more 
%reliably through intrinsic magnitudes that are anomalously lower (brighter)
%and bluer colours than what would be expected for a single star system.
